Results

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected formula
added descriptive information on SVs

@@

We exploratory wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level 2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \\text{utility rating} + corrugator \text{ activity} \\\ self-control + NFC + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).

>>>>

Individual SVs could be determined for `r nrow(data_SV)/3` participants for all three ER strategies.
SVs ranged between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`.
In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had a SVs of 1.0, indicating a clear preference for one ER strategy.
Highest SV for distraction was reported by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))`, for distancing by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`, and for suppression by $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`.

@@

We exploratory wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level 2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).
